Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia

### 2015-05-25 nlpcc/paper.tex
再次尝试提交

\section{Introduction}
With LOD growing recent years, more and more knowledge bases are generated for information sharing. Several large-scale knowledge bases, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are well-known and often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}and so on. These knowledge bases are not only cross-domain but also multilingual, which is benefit for global knowledge sharing.

Take DBpedia as an example. It extracts structured information from Wikipedia, and has already contained approximately 38.3 million things. Right now DBpedia provides 124 versions of non-English language including Chinese. There are XXX instances and 11 classes in Chinese. Obviously, the quality of Chinese information is not enough for further research or application.

A cross-lingual knowledge base has benefit efforts on global knowledge sharing, understanding and expanding. However, to build an available knowledge base, some problems are to be addressed: (1) The imbalanced size of different language sources leads to less entities. Comparing the number of articles in English Wikipedia and that in Chinese Wikipedia, which are 5 million and 800 thousand, it's obvious that to structure a knowledge base with Chinese is more difficult. (2) The number of existing cross-lingual links in Wikipedia is so small, which affects the quality of a bilingual knowledge base. Especially there is no evident links in properties. Statistically, only XX thousand cross-lingual links are there between English and Chinese articles. (3) The large but not rigorous category system in Wikipedia causes incorrect semantic relations in taxonomy. For example,\textcolor{red}{example}

@@

Currently, there are several massive knowledge encyclopedias in Chinese, including Hudong Baike and Baidu Baike. To solve the unbalance problem, we utilize such separated sources to enrich our Chinese information. In this paper, we propose an approach to combine four resources, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX concepts, XXX instances and XXX properties. To get a more available result, we also make judgement on the relation among concepts and instances. At last, a query interface is provided to access the knowledge base. Specifically, our work makes the following contributions:
\begin{itemize}
  \item We propose a method to build a Chinese-English cross-lingual knowledge base combining multi-encyclopedias. Among them, two  Chinese encyclopedias are utilized to helps balance and enrich information of two languages.
  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and analysing templates in Wikipedia for property.
  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise subClassOf and instanceOf relation in ontology.
  \item A website is developed based on our ontology and also a SPARQL interface is provided for public query operations in our knowledge base.
\end{itemize}

>>>>

\section{Introduction}
With Linked Open Data(LOD) developing recent years, an increasing number of knowledge bases are generated for information sharing. Large-scale knowledge bases in LOD project, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge}and many other applications. These knowledge bases are not only cross-domain but also multilingual, which is benefit for global knowledge sharing.

Take DBpedia as an example, it extracts structured information from Wikipedia and has already contained approximately 38.3 million things. Now DBpedia provides 124 versions of non-English language including Chinese. However, there are only XXX instances and 11 classes in Chinese. Obviously, the quality of Chinese information is insufficient for further research and application.

A cross-lingual knowledge base has positive effect on global knowledge sharing, understanding and expanding. However, to build an available knowledge base, some problems must be addressed: (1) The imbalanced size of different language sources leads to less entities. Comparing the number of articles in English Wikipedia and those in Chinese Wikipedia, which are 5 million and 800 thousand separately, it's obvious that to structure a knowledge base in Chinese with Wikipedia is more challenging. (2) The number of existing cross-lingual links in Wikipedia accounts for a low proportion, which affects the quality of a bilingual knowledge base. Especially there is no evident links in properties. Statistically, only XX thousand cross-lingual links can be found between English and Chinese articles. (3) The large but not rigorous category system in Wikipedia causes incorrect semantic relations in taxonomy. For example,\textcolor{red}{example}

@@

Currently, there are several massive knowledge encyclopedias in Chinese, including Hudong Baike and Baidu Baike. To solve the imbalance problem, we utilize such separated sources to enrich our Chinese information. In this paper, we propose an approach to combine four resources, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX concepts, XXX instances and XXX properties. To get a more available result, we also make judgement on the relation among concepts and instances. At last, a query interface is provided to access the knowledge base. Specifically, our work makes the following contributions:
\begin{itemize}
  \item We propose a method to build a Chinese-English cross-lingual knowledge base combining multi-encyclopedias. Among them, two  Chinese encyclopedias are utilized to helps balance and enrich information of two languages.
  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for concept and instance, and analysing templates in Wikipedia for property.
  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise subClassOf and instanceOf relation in ontology.
  \item A website is developed based on our ontology and also a SPARQL interface is provided for public query operations in our knowledge base.
\end{itemize}
